---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "
Is prediction of species richness from Stacked Species Distribution Models biased by habitat saturation?"
```

# Is prediction of species richness from Stacked Species Distribution Models biased by habitat saturation?

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/224002794.svg)](https://zenodo.org/badge/latestdoi/224002794) [![Launch Rstudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/Rekyt/ssdms_saturation_richness/master?urlpath=rstudio)
<!-- badges: end -->

This repository contains the data and code for our paper:

> Grenié M., Violle C, Munoz F. _`r Title`_. accepted in _Ecological Indicators_.


## How to cite

Please cite this compendium as:

> Grenié M., Violle C, Munoz F., (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.3552836>

## 🔧 How to download or install

You can download the compendium as a zip from from this URL: </archive/master.zip>

Or you can install this compendium as an R package, `cssdms.saturation.richness, from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("Rekyt/ssdms_saturation_richness")
```

## 💻 How to run the analyses

This compendium uses [`drake`](https://docs.ropensci.org/drake/) to make analyses reproducible.
To redo the analyses and rebuild the manuscript run the following lines (from the `comsat` folder):

```{r run-analyses, eval = FALSE}
# install.packages("devtools")
pkgload::load_all()  # Load all functions included in the package
make(saturation_workflow())  # Run Analyses
```

Beware that some code make time a long time to run, and it may be useful to run analyses in parallel.

##You can run the analyses by clicking on the `Binder` badge: [![Launch Rstudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/Rekyt/ssdms_saturation_richness/master?urlpath=rstudio)

 Dependencies

As noted in the `DESCRPTION` files this project depends on:

* [`virtualspecies`](https://cran.r-project.org/package=virtualspecies), to simulate species;
* [`drake`](https://cran.r-project.org/package=drake), to execute a reproducible workflow;
* the `tidyverse` (`dplyr`, `ggplot2`, `purrr`, and `tidyr`) for data wrangling;
* [`ggpubr`](https://cran.r-project.org/package=ggpubr) to customize plot
